---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# powsimR: Power analysis for bulk and single cell RNA-seq experiments

## Installation Guide

To install powsimR, make sure you have installed the following R packages:

```{r, echo=T, eval=F, tidy=T}
ipak <- function(pkg, repository=c('CRAN', 'Bioconductor', 'github')){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) {
    if(repository=='CRAN') {
      install.packages(new.pkg, dependencies = TRUE)
    }
    if(repository=='Bioconductor') {
      source("https://bioconductor.org/biocLite.R")
      biocLite(new.pkg, dependencies=TRUE, ask=FALSE)
    }
    if(repository=='github') {
      devtools::install_github(pkg, build_vignettes = FALSE)
    }
  }
}

# CRAN PACKAGES
cranpackages <- c("gamlss.dist", "methods", "stats", "moments", "doParallel", "parallel", "reshape2", "dplyr", "tidyr", "data.table", 'ggplot2', 'ggthemes', 'ggExtra', 'cowplot', 'scales', 'fitdistrplus', 'MASS', 'pscl', 'nonnest2', 'cobs', 'msir', 'drc', 'devtools', 'XML', 'splines')
ipak(cranpackages, repository='CRAN')

# BIOCONDUCTOR
biocpackages <- c('S4Vectors', 'AnnotationDbi', 'Biobase', 'BiocParallel', 'BiocStyle', 'scater', 'scran', 'edgeR', 'limma', 'DESeq2', 'baySeq', 'NOISeq', 'EBSeq', 'DSS', 'MAST', 'ROTS', "IHW", 'qvalue')
ipak(biocpackages, repository='Bioconductor')

# GITHUB
githubpackages <- c('gu-mi/NBGOF', 'hms-dbmi/scde', 'nghiavtr/BPSC')
ipak(githubpackages, repository = 'github')
devtools::install_github('kdkorthauer/scDD', build_vignettes = FALSE, ref = 'develop')
```

After installing the dependencies, powsim can be installed by using devtools as well.

```{r, echo=T, eval=F, tidy=T}
devtools::install_github('bvieth/powsimR', build_vignettes = TRUE)
```

## User Guide

For examples and tips on using the package, please see the vignette PDF 
[here](https://github.com/bvieth/powsim/tree/master/vignettes/powsim.pdf) 
or open it in R by typing
```{r, echo=T, eval=F, tidy=T}
browseVignettes('powsimR')
```

A preprint paper describing powsim is now on [bioRxiv](https://doi.org/10.1101/117150).

## Notes

Please send bug reports and feature requests by opening a new issue on 
[this page](https://github.com/bvieth/powsimR/issues).

Note that the error "maximal number of DLLs reached..." might occur due to the loading of many shared objects by Bioconductor packages. Restarting the R session after installing dependencies / powsimR will help.

## R Session Info

```{r}
sessionInfo()
```


